Supporting Information : Complex and informative dependencies propogate throughout ecology and can be revealed using copulas

### 2019-05-13 SupportingInformation.Rmd

# From causes to consequences for green spruce aphid abundance data\label{sect:greenspruce}

For each locations (selected based on a threshold of 30 years of data, see \ref{Data_details}), 
we computed yearwise average temperature of winter season (spanning over 4 months from December, previous 
year to March, present year). With this winter temperature time series and green spruce aphid abundance time series data 
a bivariate copula was made for each selected locations and shown in Fig. \ref{fig:greenspruce} whenever it was 
significantly dependent with a p-value $<0.05$. Stronger lower tail dependence
was visually prominent in those copulas. We used our model selection and non-parametric statistical tools 
(see Table \ref{tab:greenspruce}) to confirm our hypothesis that winter temperature 
was the main driver in "lower tail dependence" of the green
spruce aphid abundance copula from any two location pairs (see Table \ref{tab_count_LTmUT}).

>>>>

# From causes to consequences for green spruce aphid abundance, details \label{sect:greenspruce}
Winter temperature for year $t$ was for December of year $t-1$ to March of 
year $t$. Data, which pertained to the same locations and years as the aphid data,
were obtained and processed exactly as in [@Sheppard2016]. Copulas
with winter temperature are in Fig. \ref{fig:greenspruce}. Results of analyses of these
copulas that paralleled the analyses applied to bivariate ecological datasets 
(see section on methods for the observational hypotheses) are in Table \ref{tab:greenspruce}.
